---
title: "restaurant_r"
author: "sonal_soni"
date: '2022-06-26'
output: html_document
---

to read the csv file and store it in re, it is used for large data

```{r}
re <- read.csv(file.choose(), header = TRUE, sep = ",");
```

display the contents of the re. All the observations and variables will be displayed 
```{r}
re;
```

Search command gives a list of packages loaded
```{r}
search();
```

head() function in R returns the fist part of the vector , matrix , table ,data frame or function that is passed to it as a parameter. generally 
it returns first six values 
```{r}
head(re);
```

tail() function in R returns the last part of the vector, matrix , table , data frame or function that is passed to it as a parameter .
generally it returns last six values.
```{r}
tail(re);
```

head() returns first part of the dataframe . generally it returns first 6 rows but here we are specifying that first 10 rows must be printed 
```{r}
head(re,10);
```

tail() returns last part of the dataframe . generally it returns last 6 rows but here we are specifying that last 10 rows must be printed 
```{r}
tail(re,10);
```

Structure of the dataframe . str() command is used to examine the structure of the object , also gives the number of observations and 
number of variables along with data types 
```{r}
str(re);
```

it will give names of the columns 
```{r}
names(re);
```

used to return a vector of character strings containing all the variables and functions in that directory
```{r}
ls();
```

it gives the names of the columns of data frame re
```{r}
colnames(re);
```

it gives the names of the columns of data frame re
```{r}
rownames(re);
```

displays the summary of the dataframe 
```{r}
summary(re);
```

class() command is used to obtain information about the type of the object 
```{r}
class(re);
```

it gives the sum of the columns 
```{r}
colSums(is.na(re));
```

prints the maximum value in column liked in re dataframe 
```{r}
max(re$Liked);
```

prints the minimum value in column Liked in RE dataframe 
```{r}
min(re$Liked);
```

prints the median of the Liked column in Re dataframe 
```{r}
median(re$Liked);
```

prints the mean of the Liked column in Re dataframe 
```{r}
mean(re$Liked);
```

prints the mode of the Liked column in Re dataframe
```{r}
mode(re$Liked);
```

sort function returns the results sorted in ascending order . we can use minus sign to get results in descending order
```{r}
sort(re$Review);
```

order function in R returns the position of each element of its input in acsneding or descending order 
```{r}
order(re$Review);
```

rank function will return a dataframe providing the rank of each element within a dataframe  
```{r}
rank(re$Review);
```

gives both rows and columns of dataframes re
```{r}
dimnames(re);
```

prdict() function in R is used to predict the data based on input values
```{r}
predictor=c(rep('open',3),rep('closed',2));
```
```{r}
predictor;
```

prints the length of the review column
```{r}
length(re$Review);
```

the with function evaluates an R expression in an environment constructed based on dataframe 
```{r}
ww=with(re,order(re$Review,re$Liked));
```

prints the entries of ww object
```{r}
ww;
```

class() command is used to obtain the information about the type of the object
```{r}
class(re);
```

conversion of data frame to matrix 
```{r}
re.mat=as.matrix(re);
```

prints the entries of re object 
```{r}
re.mat;
```

conversion of data frame to list 
```{r}
frame.list=as.list(re);
```

prints the entries of re object 
```{r}
frame.list;
```

gives the value of standard deviation for Liked column  
```{r}
sd(re$Liked,na.rm=TRUE);
```

na.omit - used to strip out NA items 
```{r}
length(na.omit(re$Review));
```

the log() function returns the logarithm of the value in the base . by default , this function produces the natural logarithm value of the re
```{r}
log(re$Liked);
```

it rotates the data frame 
```{r}
t(re);
```

used to compute sum of table entries for a given index 
```{r}
margin.table(re$Liked);
```

it is used to calculate the value of each cell in a table as a proportion of all values 
```{r}
prop.table(re$Liked);
```

summary of the dataframe 
```{r}
summary(re);
```

used to examine the structure of the object 
```{r}
str(re);
```

it will recall the last 25 commands 
```{r}
history(re);
```

prints the first column in re object 
```{r}
re[1];
```

prints the first two columns of dataframe re
```{r}
re[1:2];
```

prints all columns except first column of dataframe re
```{r}
re[-1];
```

prints only selected columns and all rows in datframe re 
```{r}
re[c(2)];
```

prints the total columns in re dataframe 
```{r}
length(re);
```


```{r}
re[(length(re)-2):length(re)];
```

the seq R function generates a sequence of numeric value 
```{r}
re[seq(1,length(re),2)];
```

sort function returns the results sorted in ascending order 
```{r}
sort(re$Review);
```

sorts Liked column
```{r}
sort(re$Liked);
```

order function returns the position of each element in ascending or descending order 
```{r}
order(re$Review);
```


```{r}
order(re$Liked);
```

prints the value present in first row and second column 
```{r}
re[1,2];
```

prints the value present in second row , of all two columns in re dataframe
```{r}
re[2,1:2];
```

prints values of all rows in second column 
```{r}
re[,2];
```

only the specified rows and all the columns except second column will be printed 
```{r}
re[c(55,3),-2];
```

here the column is specified as Liked , only that columns specified rows will be printed 
```{r}
re[c(3,4),"Liked"];
```

all rows of column two will be printed 
```{r}
re[2];
```

all column values of specified rows will be printed 
```{r}
re[c(1,2)];
```

we are using order function on Liked column 
```{r}
order(re$Liked,re[,2]);
```

the with function evaluates an R expression in an environment constuct based on dataframe 
```{r}
with(re,order(re$Liked));
```

prints all the rows of Liked column 
```{r}
re$Liked;
```

prints only the first four rows of Liked column 
```{r}
re$Liked[1:4];
```

the with function evaluates an R expression and prints all the values in Liked column 
```{r}
with(re,Liked);
```

prints the column names 
```{r}
names(re);
```

the quantile() function in R can be used to calculate the sample quantiles of the dataset 
```{r}
quantile(re$Liked);
```

to calculate the five number summary in the R programming language we use fivenum() function 
```{r}
fivenum(re$Liked);
```

calculate quantile at 20%
```{r}
quantile(re$Liked,0.2);
```

calculate quantiles at 30%,80%,90%
```{r}
quantile(re$Liked,c(0.3,0.8,0.9));
```

calculate quantiles at 50%,75%,25%
```{r}
quantile(re$Liked,c(0.5,0.75,0.25));
```

gives cummulative sum of Liked column 
```{r}
cumsum(re$Liked);
```

gives cummulative max of Liked column
```{r}
cummax(re$Liked);
```

gives cummulative min of Liked column 
```{r}
cummin(re$Liked);
```

gives cummulative product values of Liked column 
```{r}
cumprod(re$Liked);
```


```{r}
seq=(along=re);
```


```{r}
seq_along(re);
```


```{r}
seq(from=1,to=10,by=2);
```

loading dplyr library and adding new column to the re datframe . we use mutate function to add new column 
```{r}
library(dplyr);
re %>% mutate(newcol=1);
```

for reodering we use select function . here we are selecting Liked to be first column and everything to be intact 
```{r}
re %>% select(Liked,everything());
```

selecting only value of Liked having 1
```{r}
re %>% filter(Liked==1);
```

renaming the existing column name. for that we use rename function 
```{r}
re %>% rename(Likes=Liked);
```

visuaalization of points 
```{r}
library(ggplot2);
ggplot(re,aes(x=Liked,y=Liked))+geom_point();
```


```{r}
library(dplyr);
dislike<- rep(c(100),1);
re %>% mutate(newcol1=dislike);
```


```{r}
colnames(re);
```

visualisation of line graph 
```{r}
library(ggplot2);
ggplot(re,aes(x=Liked,y=Liked))+geom_line();
```

visualisation of points on line graph 
```{r}
library(ggplot2);
ggplot(re,aes(x=Liked,y=Liked))+geom_line()+geom_point();
```

visualisation of bar graph of values
```{r}
ggplot(re,aes(x=Liked,y=Liked))+geom_col();
```

visualisation of bar graphs of Liked 
```{r}
ggplot(re,aes(x=Liked))+geom_bar();
```


```{r}
ggplot(re,aes(x=Liked))+geom_histogram(binwidth=5);
```
